---
title: "Alcohol vs Seat choice"
author: "Amber Walker"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```


## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??


```{r}
ggplot(davisdata, aes(x = Seat, y = alcohol)) +
  geom_boxplot(notch = TRUE, outlier.colour = "red") +
  labs(title = "Notched Box Plot of Alcohol by Seat") +
  theme(plot.title = element_text(hjust = 0.5))
```




## Now with ggplot - first select the basic data

  
  


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
The people in the front are drinking a lot more that the people in the middle and the front. The data shows that min all equals 0, but with the median, the people in the back have 4 and the people in the middle have 1 while the from people have none. There is a big difference between the means with the most people having the highest of almost a 10 rounded up while the people in the middle have 3 and front have a 2 rounded up.Theres 83 people sitting in the middle.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
```{r}
plot(TukeyHSD(model1))
```
```{r}
# Load the necessary library
library(stats)

# Perform ANOVA test
anova_result <- aov(alcohol ~ Seat, data = davisdata)

# Check the ANOVA table
summary(anova_result)
```



```{r}
# Perform Tukey HSD test
tukey_result <- TukeyHSD(anova_result)

# Print the results
print(tukey_result)

```


## Conclusions


